To Do List

### 2019-11-02 Papers.Rmd
Add note that Conservation, GC content, distanceB  to TSS did NOT improve predictions

- Yan, Koon-Kiu, Shaoke Lou, and Mark Gerstein. “MrTADFinder: A Network Modularity Based Approach to Identify Topologically Associating Domains in Multiple Resolutions.” PLoS Computational Biology 13, no. 7 (July 2017): e1005647. https://doi.org/10.1371/journal.pcbi.1005647. - MrTADFinder - network modularity-based TAD finder, community detection. Adapted for multiple resolutions with parameter y. Distance-dependent model. Optimization framework, Louvain algorithm to optimize Q. Confirmed Dixon's observations of H3K4me3, H3K27ac enrichment at TAD boundaries, depletion of H3K9me3, H3K27me3 enriched across resolutions. Genes, especially, housekeeping, are enriched near TAD boundaries. High- and extreme occupancy target regions (TF binding) are also enriched. CTCF enrichment is general. Logistic regression to predict TAD boundaries from TFBSs, prioritize which TFs are most important, Refs 18 and 19 refer to similar work. https://github.com/gersteinlab/MrTADFinder

@@

@@

- Singh, Shashank, Yang Yang, Barnabas Poczos, and Jian Ma. “Predicting Enhancer-Promoter Interaction from Genomic Sequence with Deep Neural Networks,” February 5, 2018. https://doi.org/10.1101/085241. - SPEID - predict enhancer-promoter interactions from sequence only using deep learning. Extends author's PEP work, compared with TargetFinder, not RIPPLE. Three layers, convolutional, recurrent, dense. AUROC, F1. Class imbalance is addressed by "data augmentation", similar to oversampling. Ro account for proximal features, enhancers are extended. Feature importance in different cell lines. https://github.com/ma-compbio/SPEID

>>>>

- Yan, Koon-Kiu, Shaoke Lou, and Mark Gerstein. “MrTADFinder: A Network Modularity Based Approach to Identify Topologically Associating Domains in Multiple Resolutions.” PLoS Computational Biology 13, no. 7 (July 2017): e1005647. https://doi.org/10.1371/journal.pcbi.1005647. - MrTADFinder - network modularity-based TAD finder, community detection. Adapted for multiple resolutions with parameter y. Distance-dependent model. Optimization framework, Louvain algorithm to optimize Q. Confirmed Dixons observations of H3K4me3, H3K27ac enrichment at TAD boundaries, depletion of H3K9me3, H3K27me3 enriched across resolutions. Genes, especially, housekeeping, are enriched near TAD boundaries. High- and extreme occupancy target regions (TF binding) are also enriched. CTCF enrichment is general. Logistic regression to predict TAD boundaries from TFBSs, prioritize which TFs are most important, Refs 18 and 19 refer to similar work. https://github.com/gersteinlab/MrTADFinder

@@

- Conservation, GC content, distance  to TSS did NOT improve predictions. Jialiang Huang et al., “Predicting Chromatin Organization Using Histone Marks,” Genome Biology 16, no. 1 (December 2015), https://doi.org/10.1186/s13059-015-0740-z.

@@

- Singh, Shashank, Yang Yang, Barnabas Poczos, and Jian Ma. “Predicting Enhancer-Promoter Interaction from Genomic Sequence with Deep Neural Networks,” February 5, 2018. https://doi.org/10.1101/085241. - SPEID - predict enhancer-promoter interactions from sequence only using deep learning. Extends authors PEP work, compared with TargetFinder, not RIPPLE. Three layers, convolutional, recurrent, dense. AUROC, F1. Class imbalance is addressed by "data augmentation", similar to oversampling. Ro account for proximal features, enhancers are extended. Feature importance in different cell lines. https://github.com/ma-compbio/SPEID
